\section{Conclusion}

In conclusion, this paper presents a novel approach to AI-generated audio detection by leveraging phase-based analysis through the fast fourier transform (FFT). The system created by the author employs three key metrics—phase coherence, phase velocity, and spectral entropy to distinguish between human and nonhuman speech. The mathematical foundation utilizes windowing techniques to segment audio signals, applies FFT for frequency domain transformation, and extracts phase information to identify subtle artifacts in synthetic speech. These metrics are integrated through a weighted classification approach that evaluates the temporal consistency, spectral distribution, and phase relationships inherent in audio signals, providing a computationally efficient framework for deepfake detection.

However, the system exhibits certain limitations that affect its detection accuracy regarding the stability and similarity parameter since it shows no major findings. Needless to say, this system will be obsolete. The system might fail to distinguish authentic audio from synthetic speech when environmental factors such as background noise, low-quality recordings, or post-processing effects are present, as these conditions can introduce phase distortions similar. 

Several improvements are recommended to increase system's performance. First, incorporating additional spectral features such as mel-frequency cepstral coefficients (MFCCs) or formant analysis could provide complementary information to phase-based metrics. Second, implementing machine learning classifiers trained on diverse datasets would enable adaptive threshold determination and better generalization across different AI synthesis models. Third, developing noise-robust preprocessing techniques would improve performance in real-world scenarios with varying audio quality. Last but not least, there are many approaches for detecting speech deepfakes, using FFT is not always the most optimal approach. Nevertheless, as long as technology advancement is concerned, FFT is one of the most efficient algorithms to detect AI-generated speech in an optimized time.